
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\title{Chronotension Field Theory (CFT)\\Glossary of Terms \& Figure Descriptions}
\author{Luke W. Cann}
\date{July 2025}

\begin{document}
\maketitle

\section*{I. Glossary of Terms \& Symbols}

\subsection*{Core Fields and Functions}
\begin{itemize}
  \item $\eta(x, t)$ — \textbf{Viscosity Field}: Describes resistance to time flow. Higher $\eta$ slows time.
  \item $\mathcal{T}(x, t)$ — \textbf{Tension Field}: Describes structural pressure or directional resistance in the time-fluid.
  \item $a(t)$ — \textbf{Scale Factor}: Apparent expansion of space, modeled as a function of evolving $\eta(t)$.
  \item $f(\eta)$ — \textbf{Time Remapping Function}: Transforms internal time to observed time.
  \item $t_{\text{obs}}$ — \textbf{Observer Time}: Time experienced by observers in evolving viscosity field.
  \item $r$ — Radial distance from chronode center.
\end{itemize}

\subsection*{Quantum and Field-Theoretic Terms}
\begin{itemize}
  \item $\chi$ — \textbf{Chronode Field}: Soliton-like excitation of the $\eta$ field; localized compression of time.
  \item $V(\eta)$ — \textbf{Self-Interaction Potential}: Governs nonlinear behavior of the $\eta$ field.
  \item $\mathcal{L}_{\text{CFT}}$ — \textbf{Lagrangian Density} of the CFT system.
  \item $\mathcal{L}_{\text{int}}$ — \textbf{Interaction Lagrangian} between $\eta$ and $\chi$.
  \item $\hbar_\eta$ — \textbf{Viscosity-Adjusted Planck Constant}: Modified quantum limit derived from $\eta$-space uncertainty.
\end{itemize}

\subsection*{Observational Quantities}
\begin{itemize}
  \item $r_s^{\text{CFT}}$ — \textbf{Sound Horizon (BAO Ruler)}: Derived from $\eta(t)$, no dark matter required.
  \item $H(z)$ — \textbf{Hubble Parameter}: Redefined in CFT via $\eta$-adjusted remapping.
  \item $\Delta x \cdot \Delta(\partial_x \eta) \geq \hbar_\eta$ — \textbf{Modified Uncertainty Relation} in C-QFT.
  \item $T^{\mu\nu}_{\text{CFT}}$ — \textbf{Stress-energy tensor} derived from $\mathcal{L}_{\text{CFT}}$.
\end{itemize}

\section*{II. Figure Descriptions (LaTeX Ready)}

\begin{itemize}
  \item \textbf{Figure 1: Viscosity Decay Curve} — ``Viscosity $\eta(t)$ over cosmic time showing exponential decay. Key parameter $\beta$ controls decay sharpness.''
  \item \textbf{Figure 2: Observer Time Remapping Function} — ``Time remapping function $f(\eta)$, showing nonlinear transition between internal and observed time.''
  \item \textbf{Figure 3: Expansion Curve vs Observational Data} — ``Predicted scale factor $a(t)$ from CFT compared to supernova Ia data (Pantheon+).''
  \item \textbf{Figure 4: BAO Sound Horizon Derivation} — ``Integral solution for CFT sound horizon $r_s^{\text{CFT}}$, consistent with observed BAO peak at $\sim 128.4$ Mpc.''
  \item \textbf{Figure 5: Chronode Field Profile} — ``Simulated spatial profile of a Chronode — a stable, localized compression in the $\eta(x,t)$ field.''
  \item \textbf{Figure 6: Lensing via $\eta(x,t)$ Curvature} — ``Deflection of photon paths caused by curvature in $\eta(x,t)$, without spacetime curvature.''
\end{itemize}

\end{document}
